Community Detection Methods for Generalized Random Dot Product Graphs

### 2021-06-01 proposal/proposal.Rmd
found another typo

As discussed in \S 2.2, all Bernoulli graph models can be expressed as a RDPG or GRDPG model, and in particular, the (associative) SBM is a RDPG with a very specific structure in the latent space. A similar result has been shown for the DCBM \cite{lyzinski2014}. We can also extend this to the PABM. In \S 3.1, we show that the PABM is equivalent to the GRDPG model for which the communities correspond to subspaces in the latent configuration. We further show that while the latent configuration is not unique, there exists one in particular for which the subspaces are orthogonal. This leads to two straightforward methods for community detection, one involving computing inner products in the ASE and another which is a straightforward application of an existing algorithm for subspace clustering. Finally, we will briefly explore alternative, non-spectral-based methods for community detection in the ASE involving Expectation Maximization and Bayesian methods.

>>>>

As discussed in \S 2.2, all Bernoulli graph models can be expressed as a RDPG or GRDPG model, and in particular, the (assortative) SBM is a RDPG with a very specific structure in the latent space. A similar result has been shown for the DCBM \cite{lyzinski2014}. We can also extend this to the PABM. In \S 3.1, we show that the PABM is equivalent to the GRDPG model for which the communities correspond to subspaces in the latent configuration. We further show that while the latent configuration is not unique, there exists one in particular for which the subspaces are orthogonal. This leads to two straightforward methods for community detection, one involving computing inner products in the ASE and another which is a straightforward application of an existing algorithm for subspace clustering. Finally, we will briefly explore alternative, non-spectral-based methods for community detection in the ASE involving Expectation Maximization and Bayesian methods.
